---
title: "p8105_HW5_ah3108"
author: "Ava Hamilton"
date: "11/4/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(viridis)

knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  fig.width = 10, 
  fig.height = 6
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_hue
scale_fill_discrete = scale_color_hue
theme_set(theme_minimal() + theme(legend.position = "bottom"))



```


# Problem 1

create a function that takes in a vector, replaces missing values,and returns the vector.

```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))

col1 = iris_with_missing[1]


fill_NA = function(vec_to_fill) {
  if (is.character(vec_to_fill)) {
    vec_to_fill[is.na(vec_to_fill)] = "virginica"
  } else if (is.numeric(vec_to_fill)) {
    mean_col_val = mean(vec_to_fill,na.rm = T)
    vec_to_fill[is.na(vec_to_fill)] = mean_col_val
  }
  else {
    stop("x is not a numeric or character vector")
  }
  return(vec_to_fill)
}


```

Use a mapping statement to replace missing values in the iris dataset.
```{r}

map(iris_with_missing, fill_NA)

```


# Problem 2

```{r, message = FALSE, warning= FALSE}

df_p2 = tibble(in_file = list.files(path = "./datafiles/")) 

df_p2 = df_p2 %>% 
  mutate(
    map(in_file, ~ read_csv(file.path(path = "./datafiles/", .)))
  ) %>% 
  unnest()

df_p2 = df_p2 %>% 
  separate(col = in_file, into = c("experiment_group", "subject")) %>%
  mutate(
    subject = as.numeric(subject),
    experiment_group = as.factor(experiment_group),
    experiment_group = factor(experiment_group, levels = c("con", "exp"), labels = c("Control", "Experiment")),
    subject = case_when(
      experiment_group == "Experiment" ~ subject+10,
      experiment_group == "Control" ~ subject
    ),
    grouptest = as.character(experiment_group)
  ) 


long_df_p2 = df_p2 %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "data_point"
  ) %>% 
  mutate(
    week = as.numeric(week)
  ) %>% 
  group_by(subject)


long_df_p2 %>% 
  ggplot(aes(x = week, y = data_point, color = experiment_group)) +
  geom_point() +
  geom_path() +
  theme_bw() +
  labs(
    title = "Results across week for each subject",
    x = "Week",
    y = "Observation")


```

The Control group had relatively stable observations over the 8 weeks starting with a mean of (mean = `r mean(pull(long_df_p2, data_point)[pull(long_df_p2, week) == 1 & pull(long_df_p2, experiment_group) == "Control"])`). The obersvations for subjects in the Experiment group increased across time starting with a mean of (mean = `r mean(pull(long_df_p2, data_point)[pull(long_df_p2, week) == 1 & pull(long_df_p2, experiment_group) == "Experiment"])`). By the 6th week almost all subjects in the experiment group had higher observations (mean = `r mean(pull(long_df_p2, data_point)[pull(long_df_p2, week) == 6 & pull(long_df_p2, experiment_group) == "Experiment"])`) than those in the control group (mean = `r mean(pull(long_df_p2, data_point)[pull(long_df_p2, week) == 6 & pull(long_df_p2, experiment_group) == "Control"])`). By the end of the study period, in the 8th week, all subjects in the experiment group  (mean = `r mean(pull(long_df_p2, data_point)[pull(long_df_p2, week) == 8 & pull(long_df_p2, experiment_group) == "Experiment"])`) had higher values than the control group  (mean = `r mean(pull(long_df_p2, data_point)[pull(long_df_p2, week) == 8 & pull(long_df_p2, experiment_group) == "Control"])`). 

AVA INSERT RANGES ABOVE

# Problem 3

```{r, cache = T}

# function to simulate data wtih n = 30, beta0 = 2


sim_data_fxn = function(beta1) {
  n = 30
  beta0 = 2
  # table of simulated data
  sim_data = tibble(
    x = rnorm(n, mean = 0, sd = 1),
    y = beta0 + beta1 * x + rnorm(n, 0, 50)
  )
  # run linear model and clean output
  ls_fit = lm(y ~ x, data = sim_data) %>% 
    broom::tidy() %>% 
    filter(term == "x") %>% 
    select(estimate, p.value)
}


#### large 
sim_results_large =
  tibble(beta1 = c(1, 2, 3, 4, 5, 6)) %>% 
  mutate(
    output_list = map(.x = beta1, ~rerun(10000, sim_data_fxn(beta1 = .x))),
    output_df = map(output_list, bind_rows)
  ) %>% 
  select(-output_list) %>% 
  unnest(output_df)


sim_results_large_edit = sim_results_large %>% 
  mutate(
    reject_H0 = case_when(
      p.value < 0.05 ~ 1,
      p.value >=0.05 ~ 0
    )
  )

sim_results_large_edit = sim_results_large_edit %>% 
  group_by(beta1) %>% 
  mutate(
    sum_reject_HO = sum(reject_H0),
    prop_reject_H0 = sum_reject_HO/length(sum_reject_HO)
    
  ) %>% 
  ungroup()

prob3_plot1 = sim_results_large_edit %>%
  distinct(beta1, prop_reject_H0, sum_reject_HO) %>% 
  mutate(
    perc_rej_H0 = prop_reject_H0 * 100
  )


prob3_plot1 %>% 
  ggplot(aes(x = beta1, y = perc_rej_H0, fill = beta1)) + 
  geom_bar(stat = "identity") +
  labs(
    title = "P3 - Figure 1. Reject H0 based on beta 1",
    x = "Beta 1",
    y = "% Reject HO")



prob3_plot2a = sim_results_large_edit %>% 
  group_by(beta1) %>% 
  mutate(
    avg_beta1 = mean(estimate)
  ) %>% 
  ungroup() %>% 
  distinct(beta1, avg_beta1)

prob3_plot2b = sim_results_large_edit %>% 
  filter(reject_H0 == 1) %>% 
  group_by(beta1) %>% 
  mutate(
    avg_beta1 = mean(estimate)
  ) %>% 
  ungroup() %>% 
  distinct(beta1, avg_beta1)

prob3_plot2a %>% 
  ggplot(aes(x = beta1, y = avg_beta1, color = "Total Average")) +
  geom_point(size = 4) +
  geom_point(data = prob3_plot2b, size = 4, aes(color = "Reject H0 Average")) +
  labs(
    title = "P3 - Figure 2. Estimated beta1 compared to actual beta1",
    x = "Beta1",
    y = "Estimated Beta1",
    color = "Average estimate")



```


The average estimates of beta1 when the null hypothesis was rejected are not close to the actal values of beta1. This is because the null hypothesis is testing whether the slope of the simulated data is significantly different from beta1. If the slope of the data **is** signficantly different than beta1, then the null hyptoehsis is rejected. Therefore, the average estimates of beta among the samples for which the null was rejected, are not approximately equal to the actual estimates.



