---
title: "p8105_HW5_ah3108"
author: "Ava Hamilton"
date: "11/4/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(viridis)

knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  fig.width = 10, 
  fig.height = 6
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_hue
scale_fill_discrete = scale_color_hue
theme_set(theme_minimal() + theme(legend.position = "bottom"))



```


# Problem 1

create a function that takes in a vector, replaces missing values,and returns the vector.

```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))

col1 = iris_with_missing[1]


fill_NA = function(vec_to_fill) {
  if (is.character(vec_to_fill)) {
    vec_to_fill[is.na(vec_to_fill)] = "virginica"
  } else if (is.numeric(vec_to_fill)) {
    mean_col_val = mean(vec_to_fill,na.rm = T)
    vec_to_fill[is.na(vec_to_fill)] = mean_col_val
  }
  else {
    stop("x is not a numeric or character vector")
  }
  return(vec_to_fill)
}


```

Use a mapping statement to replace missing values in the iris dataset.
```{r}

map(iris_with_missing, fill_NA)

```


# Problem 2

```{r, message = FALSE, warning= FALSE}

df_p2 = tibble(in_file = list.files(path = "./datafiles/")) 

df_p2 = df_p2 %>% 
  mutate(
    map(in_file, ~ read_csv(file.path(path = "./datafiles/", .)))
  ) %>% 
  unnest()

df_p2 = df_p2 %>% 
  separate(col = in_file, into = c("experiment_group", "subject")) %>%
  mutate(
    subject = as.numeric(subject),
    experiment_group = as.factor(experiment_group),
    experiment_group = factor(experiment_group, levels = c("con", "exp"), labels = c("Control", "Experiment")),
    subject = case_when(
      experiment_group == "Experiment" ~ subject+10,
      experiment_group == "Control" ~ subject
    ),
    grouptest = as.character(experiment_group)
  ) 


long_df_p2 = df_p2 %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "data_point"
  ) %>% 
  mutate(
    week = as.numeric(week)
  ) %>% 
  group_by(subject)


long_df_p2 %>% 
  ggplot(aes(x = week, y = data_point, color = experiment_group)) +
  geom_point() +
  geom_path() +
  theme_bw() +
  labs(
    title = "Results across week for each subject",
    x = "Week",
    y = "Observation")


#long_df_p2s = long_df_p2 %>% 
 # filter(subject %in% c(2,20))


```

The Control group had relatively stable observations over the 8 weeks. The obersvations for subjects in the Experiment group increased across time. By the 6th week almost all subjects in the experiment group had higher observations than those in the control group. By the end of the study period, in the 8th week, all subjects in the experiment group had higher values than the control group. 

AVA INSERT RANGES ABOVE

# Problem 3

```{r}

# function to simulate data wtih n = 30, beta0 = 2


sim_data = function(beta1) {
  n = 30
  beta0 = 2
  # table of simulated data
  sim_data = tibble(
    x = rnorm(n, mean = 0, sd = 1),
    y = beta0 + beta1 * x + rnorm(n, 0, 50)
  )
  # run linear model and clean output
ls_fit = lm(y ~ x, data = sim_data) %>% 
  broom::tidy() %>% 
  filter(term == "x") %>% 
  select(estimate, p.value)
  
}

test = sim_data(0)


output1 = rerun(100, sim_data(0)) %>%
  bind_rows()

 
 sim_results_small =
  tibble(beta1 = c(1, 2, 3, 4, 5, 6)) %>% 
  mutate(
    output_list = map(.x = beta1, ~rerun(10000, sim_data(beta1 = .x))),
    output_df = map(output_list, bind_rows)
  ) %>% 
  select(-output_list) %>% 
  unnest(output_df)


 sim_results_small_edit = sim_results_small %>% 
   mutate(
    reject_H0 = case_when(
       p.value < 0.05 ~ 1,
       p.value >=0.05 ~ 0
     )
   )
 
 sim_results_small_edit = sim_results_small_edit %>% 
   group_by(beta1) %>% 
   mutate(
   sum_reject_HO = sum(reject_H0),
   prop_reject_H0 = sum_reject_HO/length(sum_reject_HO)
   
   ) %>% 
   ungroup()
 
 prob3_plot = sim_results_small_edit %>%
   distinct(beta1, prop_reject_H0, sum_reject_HO)
 
 
 
 
   ggplot(aes(x = ))
 

#### large 
 sim_results_large =
  tibble(beta1 = c(1, 2, 3, 4, 5, 6)) %>% 
  mutate(
    output_list = map(.x = beta1, ~rerun(10000, sim_data(beta1 = .x))),
    output_df = map(output_list, bind_rows)
  ) %>% 
  select(-output_list) %>% 
  unnest(output_df)


 sim_results_large_edit = sim_results_large %>% 
   mutate(
    reject_H0 = case_when(
       p.value < 0.05 ~ 1,
       p.value >=0.05 ~ 0
     )
   )
 
 sim_results_large_edit = sim_results_large_edit %>% 
   group_by(beta1) %>% 
   mutate(
   sum_reject_HO = sum(reject_H0),
   prop_reject_H0 = sum_reject_HO/length(sum_reject_HO)
   
   ) %>% 
   ungroup()
 
 prob3_plot = sim_results_large_edit %>%
   distinct(beta1, prop_reject_H0, sum_reject_HO)
 
 prob3_plot %>% 
ggplot(aes(x = prop_reject_H0, y = beta1)) 
   
   
   
   
```






